---
title: "Shiny Application and Reproducible Pitch"
author: "Jianheng Zhang"
date: "06/17/2018"
output: ioslides_presentation
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

## Diamond Data Analysis Report

Diamond Data Analysis Report allow user to review the price of diamond based on the user input such as carat, Cut, Color and Clarity.

Please use PageUp/PageDown or Left/Right Arrow keys to visit the slides.

## Application Overview

- Diamonds Properties can be analysed using several Parameters: carat, Cut, Color and Clarity are some of the common parameters. The Report allow users to get the right price for the right parameters.


## Slide with Complete Reporting Appliaction

Following link is the shiny host of the Application.

https://jansen.shinyapps.io/shinyappandreproduciblepitch/

Following link is the github of the project.

https://github.com/jansenzjh/ShinyAppAndReproduciblePitch

## Data
The data set that was used in this project is diamonds data set, which is part of ggplot2 package. Containing information about 53940 diamonds with 10 variables.

```{r, echo=TRUE}
library("ggplot2")
head(diamonds)
```